Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-02-11 SPIE/article/main.tex
more corrections

mention: technology had important improvements in past 25 years
mention anniversiary of technology
mention adoption in EU and US
mention commoditization
lack of understanding of sources of improvements across 25 years
mention works by tsao (and at least two others)

    Within only 25 years of the introduction of the first commercial white light-emitting diode, efficiency has increased by three orders of magnitude while manufacturing costs have fallen by two orders of magnitude. The total market penetration in general illumination has recently exceeded 50\% in the European Union and the United States \cite{eu2019impactass}\cite{stratunl2018}. Today, the solid-state lighting markets in the US and the EU together are valued at 58.7 Bn.\$(2020) \cite{gvr2020market_us}\cite{gvr2020market_eu}. Legislation and policy aimed at increasing the adoption of solid-state light sources has been implemented around the world \cite{2009-125-EC_regulation-2012_impact}. Estimates for the electrical energy saved annually from the adoption of energy efficiency lamps ranges from 131 TWh/year in 2020 for the EU to 442 TWh/year in 2020 for the US.

>>>>

    Within only 25 years of the introduction of the first commercial white light-emitting diode, efficiency has increased by three orders of magnitude while manufacturing costs have fallen by two orders of magnitude. After legislation aimed at increasing the adoption of solid-state light sources has been implemented around the world, the solid state lighting industry has become a rare success story in the global drive for the transformation of energy systems. Estimates for the electrical energy saved annually from the adoption of energy efficiency lamps ranges from 131 TWh/year in 2020 for the EU \cite{eu2019impactass} to 442 TWh/year in 2020 for the US \cite{yamada2015adoption,guidehouse2020adoption}.

    Understanding the sources and impact of these dramatic improvements on LED manufacturing is essential for researchers, industry professionals, as well as policymakers in the sphere of energy, science and innovation, as they may provide valuable insights for the acceleration of innovation in other demand-side energy technologies. Our research aims to XXX
